---
title: "Regression"
author: "Rikita Patangay"
date: "2022-09-25"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro to Linear Regression

In linear regression the data will consist of predictor values (x) and target values (y). To find the relationship between x and y we will use linear regression. This relationship can be defined using parameters such as w and b. Regression models a target prediction value for the provided data, based on independent variables. 

Strengths:
- It is a relatively simple algorithm.
- Efficient when the data follows a linear pattern.
- Has low variance.

Weaknesses:
- High bias because it assumes a linear shape to the data.


## Read in Dataset: Weather Data

Using read.csv to read in the file and put the data set in the variable (df).

```{r}
df <- read.csv("WeatherData.csv")
str(df)
```




## a.) Split data 80/20

Here I am dividing the data in training and test sets. This works by randomly sampling the data using the sample() function. This is an 80/20 split.

```{r}
set.seed(1234)
i <- sample(1:nrow(df), .80*nrow(df), replace=FALSE)
train <- df[i,]
test <- df[-i,]
```




## b.) 5 Functions
These are 5 pretty simple functions used for data exploration.

head() - gives some of the start of the data sample

tail() - gives some of the end of the data sample 

nrow() - gives number of rows in the sample

ncol() - gives number of columns in the sample\

summary() - gives a brief summary of values associated with the data.

```{r}
head(train)
```
```{r}
tail(train)
```
```{r}
nrow(train)
```
```{r}
ncol(train)
```
```{r}
summary(train)
```



## c.) 2 Informative Graphs
These are two infromative graphs. The first one is a histogram and the second is scatterplot.

```{r}
hist(train$Rel.Hum_., breaks=12, col="red")
```
```{r}
attach(train)
plot(Rel.Hum_., Temp_C, main="Scatterplot of Relative Humidity",
   xlab="Relative Humidity ", ylab="Temperature in Celsius ", pch=19)
```




## d.) Build a Simple Regression Model

Here we are building a simple regression model. What we are doing in the model is using the predictor which would be the Rel.Hum. Which is the relative humidity, and our target (y) is Visibility.



Call:
lm(formula = Rel.Hum_. ~ Visibility_km, data = train)

Residuals:
Min:-48.806  1Q: -8.806   Median: 0.427  3Q: 9.194  Max: 50.039 
         

Coefficients:
(Estimate Std., Error, t value, Pr(>|t|)<-- corresponds with numbers below)    
(Intercept)   91.09954,    0.37749,  241.33,   <2e-16 ***
Visibility_km -0.85173,    0.01241,  -68.65,   <2e-16 ***

Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

Residual standard error: 13.09 on 7025 degrees of freedom

Multiple R-squared:  0.4015,	Adjusted R-squared:  0.4014 

F-statistic:  4712 on 1 and 7025 DF

p-value: < 2.2e-16





## e.)


Could not figure out residual plots :(



## f.) Multiple Regression Model

Here we are building a multiple regression model. What we are doing in the model is using the predictor which would be the Rel.Hum. Which is the relative humidity, and our target (y) is Temp_C which is temperature in Celsius. We can use the data to compare the levels of Temp/Humidity and how they correlate.



Call:
lm(formula = Rel.Hum_. ~ Temp_C, data = train)

Residuals:
Min: -49.966
1Q: -12.004
Median: 0.735
3Q: 13.177
Max: 34.096 
       

Coefficients:

(Estimate Std., Error, t value, Pr(>|t|) <-- corresponds with numbers below)

(Intercept) 70.20387,   0.24781,  283.30,   <2e-16 ***

Temp_C      -0.30494,    0.01695,  -17.99,   <2e-16 ***

Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

Residual standard error: 16.55 on 7025 degrees of freedom

Multiple R-squared:  0.04405,	Adjusted R-squared:  0.04391 

F-statistic: 323.7 on 1 and 7025 DF
p-value: < 2.2e-16




## g.) Third Regression Model

Here we are building another regression model. What we are doing in the model is using the predictor which would be the Wind.Speed_km.h. Which is the Wind Speed in kilometers/hr, and our target (y) is Visibility_km which is the visibility in km We can use the data to compare the levels of Visibility/Wind Speed and how they correlate.




Call:
lm(formula = Wind.Speed_km.h ~ Visibility_km, data = train)

Residuals:

Min: -15.022  1Q: -6.022  Median: -1.926 3Q: 5.036  Max: 68.036 
        68.036 

Coefficients:

(Estimate Std., Error, t value, Pr(>|t|)<-- corresponds with numbers below)  

(Intercept)   14.901389,   0.251386,  59.277,   <2e-16 ***

Visibility_km  0.002507,   0.008263,   0.303,    0.762    

Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1


## h.) Comparing the results

I think that the multiple regression is the most accuate because it shows the correlation of multiple variables, and the correlation between them.

## i.) Predict and evaluate



